Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex
paper: almost there.. conclusions are out

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. The probability that a user
prefers configuration $\vx^i$ over $\vx^j$ is defined according to the
classical (without indifference) Bradley-Terry model~\cite{BraTer52} as:
%
$$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
where $\vw$ is the weight vector of the true underlying user utility.
Support for indifference is modelled as an exponential distribution
over the closeness of the two utilities:
%
$$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|). $$
%
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations, as in~\cite{guo2010real}.
% \footnote{When experimenting with EUS and QI, the user is
%   forced to select its preffered item, so indifference is not
%   possible. While support for indifference could be added, we chose to
%   be consistent with the methods as originally published.}, as

@@

A PC configurations is defined by eight attributes: computer type (laptop,
desktop, or tower), manufacturer (8 choices), CPU model (37), monitor size (8), RAM amount (10), storage (10)
size, and price.
%See Table~\ref{tab:pcdataset} for an overivew of the attributes.
The price attribute is defined as a linear combination of the other
attributes: this is a fair modeling choice, as often the price of a PC is
well approximated by the sum of the price of its components plus a bias due to
branding.
%
Interactions between attributes are expressed as Horn clauses. An example
constraint might look like this: ``if the manufacturer is Apple, then the
CPU must be either a PowerPC G3 or a PowerPC G4''%
%\footnote{Despite the components
%included in the dataset, which are a bit outdated, the dataset itself is pretty
%realistic.} \andrea{necessario?}
, which can be encoded into MILP form as
%
$ (1 - x_\text{Apple}) + x_\text{G3} + x_\text{G4} \ge 1 $.
%
Note that mutual exclusivity between all binary variables of the
one-hot encoding of an attribute ensures that only one of
$x_\text{G3}$ and $x_\text{G4}$ can be 1.  The dataset includes
constraints between the following attributes: manufacturer $\to$ type,
manufacturer $\to$ CPU, type $\to$ RAM amount, type $\to$ storage
size, type $\to$ monitor size, for 16 Horn constraints total. We do
not report the full list due to space limitations. Note that the
search space is of the order of hundreds of thousands of candidate
configurations, and is far beyond reach of existing Bayesian
approaches.

@@

We presented a max-margin approach for efficient preference
elicitation in large configuration spaces. Our approach relies on an
extension of max-margin learning to sets, and is
effective in the generation of a diverse set of configurations that can be used
to ask informative preference queries.  The main advantages of this
elicitation method are 1) its ability to elicit preferences and
provide recommendations in large configuration problems 2)
robustness with respect to erroneous feedback and 3)  ability to
encourage sparse utility functions. 
Experimental comparisons against
state-of-the-art Bayesian preference elicitation strategies confirm
its substantial computational advantages. For sparse utility
functions, the method compares favorably also in terms of utility loss.
%the number
%of queries asked to the user.

>>>>

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. The probability that a user
prefers configuration $\vx^i$ over $\vx^j$ is defined according to the
classical (without indifference) Bradley-Terry model~\cite{BraTer52} as
$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $,
where $\vw$ is the weight vector of the true underlying user utility.
Support for indifference is modelled as an exponential distribution
over the closeness of the two utilities, i.e. 
$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|).$
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations, as in~\cite{guo2010real}.
% \footnote{When experimenting with EUS and QI, the user is
%   forced to select its preffered item, so indifference is not
%   possible. While support for indifference could be added, we chose to
%   be consistent with the methods as originally published.}, as

@@

A PC configurations is defined by eight attributes: computer type (laptop,
desktop, or tower), manufacturer (8 choices), CPU model (37), monitor size (8), RAM amount (10), storage (10)
size, and price.
%See Table~\ref{tab:pcdataset} for an overivew of the attributes.
The price attribute is defined as a linear combination of the other
attributes: this is a fair modeling choice, as often the price of a PC is
well approximated by the sum of the price of its components plus a bias due to
branding.
%
Interactions between attributes are expressed as Horn clauses. An example
constraint might look like this: ``if the manufacturer is Apple, then the
CPU must be either a PowerPC G3 or a PowerPC G4''%
%\footnote{Despite the components
%included in the dataset, which are a bit outdated, the dataset itself is pretty
%realistic.} \andrea{necessario?}
, which can be encoded into MILP form as
%
$ (1 - x_\text{Apple}) + x_\text{G3} + x_\text{G4} \ge 1 $.
%
Note that only one of $x_\text{G3}$ and $x_\text{G4}$ can be 1 because
of the mutual exclusivity constraints of the one-hot encoding.  The
dataset includes constraints between the following attributes:
manufacturer $\to$ type, manufacturer $\to$ CPU, type $\to$ RAM
amount, type $\to$ storage size, type $\to$ monitor size, for 16 Horn
constraints total. We do not report the full list due to space
limitations. Note that the search space is of the order of hundreds of
thousands of candidate configurations, and is far beyond reach of
existing Bayesian approaches.

@@

We presented a max-margin approach for efficient preference
elicitation in large configuration spaces. Our approach relies on an
extension of max-margin learning to sets, and is
effective in the generation of a diverse set of configurations that can be used
to ask informative preference queries.  The main advantages of this
elicitation method are 1) its ability to elicit preferences and
provide recommendations in large configuration problems 2)
robustness with respect to erroneous feedback and 3)  ability to
encourage sparse utility functions. 
Experimental comparisons against
state-of-the-art Bayesian preference elicitation strategies confirm
its substantial computational advantages. For sparse utility
functions, the method compares favorably also in terms of utility loss.

\FloatBarrier
